Directionality in Kilo-ton Scale Scintillating Neutrino Detectors

### 2013-07-15 Direction.tex
More files. --Lindley

% All university affiliations addresses go here:
\newcommand{\ucla}{\affiliation{University of California Los Angeles, Los Angeles, CA 90049, USA}}
\newcommand{\chicago}{\affiliation{University of Chicago, Chicago, IL, XXXX, USA}}

>>>>

% All university affiliations addresses go here:
\newcommand{\ucla}{\affiliation{University of California Los Angeles, Los Angeles, CA 90095, USA}}
\newcommand{\chicago}{\affiliation{University of Chicago, Chicago, IL, 60637, USA}}
